Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-04-06 paper/01-introduction.tex
first draft of sec analysis section (5)
sec analysis changes
Updates

In ICN (or more specifically, CCN and NDN), ANDaNA was the first anonymity network of its
kind. Similar to Tor, ANDaNA uses circuits formed from anonymizing routers (ARs)
to marshall requests and responses between consumers and producers. The former
onion-encrypt interests and content using the public key(s) of the target ARs.
A variant of ANDaNA uses symmetric keys for packet encapsulation but suffers from
linkability. Tsudik et al. \cite{ac3n} proposed an optimized version of the symmetric-key
ANDaNA variant that did not permit linkability. To the best of our knowledge, there
is no anonymity network variant for ICN architectures. Though tunneling is only
useful for only a subset of ICN traffic, we believe it is a gap to be addressed
for this emerging technology, for a variety of reasons. {\bf First}, privacy
continues to be an elusive property for CCN applications. Tunneling will help
permit some degree of privacy within trusted AS domains from external passive
eavesdroppers. {\bf Second}, multi-hop circuits as used in ANDaNA are overkill
when trying to retain privacy instead of anonymity. {\bf Third}, end-to-end
sessions such as those enabled by CCNxKE \cite{ccnxke} and similar protocols
only serve those engaged in the session. In contrast, since the threat model is
different, tunneled traffic has the potential to serve any number of consumers
within the same trusted domain. Thus, while tunneling may contrast the content-centric
nature of data transmission in CCN, it fills a needed void for this architecture.

@@

XXX

>>>>

In ICN (or more specifically, CCN and NDN), ANDaNA was the first anonymity network of its
kind. Similar to Tor, ANDaNA uses circuits formed from anonymizing routers (ARs)
to marshall requests and responses between consumers and producers. The former
onion-encrypt interests and content using the public key(s) of the target ARs.
A variant of ANDaNA uses symmetric keys for packet encapsulation but suffers from
linkability. Tsudik et al. \cite{tsudik2016ac3n} proposed an optimized version of the symmetric-key
ANDaNA variant that did not permit linkability. To the best of our knowledge, there
is no anonymity network variant for ICN architectures. Though tunneling is only
useful for only a subset of ICN traffic, we believe it is a gap to be addressed
for this emerging technology, for a variety of reasons. {\bf First}, privacy
continues to be an elusive property for CCN applications. Tunneling will help
permit some degree of privacy within trusted AS domains from external passive
eavesdroppers. {\bf Second}, multi-hop circuits as used in ANDaNA are overkill
when trying to retain privacy instead of anonymity. {\bf Third}, end-to-end
sessions such as those enabled by CCNxKE \cite{ccnxke} and similar protocols
only serve those engaged in the session. In contrast, since the threat model is
different, tunneled traffic has the potential to serve any number of consumers
within the same trusted domain. Thus, while tunneling may contrast the content-centric
nature of data transmission in CCN, it fills a needed void for this architecture.

@@

The rest of this paper is organized as follows. Section \ref{sec:prelims} provides
an overview of CCN and the relevant protocol details necessary to understand
CCVPN. Section \ref{sec:related} describes previous related work that motivates
our design. Section \ref{metho} then describes the main CCVPN design with the necessary
cryptographic and packet format details. We analyze the security of CCVPN
in Section \ref{sec:sec-analysis}. We present the results of a comprehensive
analysis and experimental evaluation in Sections \ref{sec:analysis} and \ref{sec:exp},
respectively. We then conclude with a discussion of future work in Section \ref{sec:conclusion}

### 2017-04-06 paper/02-overview.tex
Updates

\section{Preliminaries}
This section presents an overview of the CCN architecture\footnote{Named-Data Networking \cite{jacobson2009networking}
is an ICN architecture related to CCN. However, since CCNxKE was
designed for ICNs that have features which are not supported by NDN (such
as exact name matching), we do not focus on NDN in this work. However,
CCNx could be retrofitted to work for NDN as well.} and work
related to confidentiality, privacy, and transport security. Those familiar with these topics
can skip it without loss of continuity.

>>>>

\section{Preliminaries}\label{sec:prelims}
This section presents an overview of the CCN architecture\footnote{Named-Data Networking \cite{jacobson2009networking}
is an ICN architecture related to CCN. However, since CCNxKE was
designed for ICNs that have features which are not supported by NDN (such
as exact name matching), we do not focus on NDN in this work. However,
CCNx could be retrofitted to work for NDN as well.} and work
related to confidentiality, privacy, and transport security. Those familiar with these topics
can skip it without loss of continuity.

### 2017-04-06 paper/05-sec-analysis.tex
Updates

Another use case for CCVPN is the traditional VPN use case, in which two physically separated local networks (for instances to offices of the same company in different countries) should virtually behave as a private local network. In that case, it is necessary to prevent that a given $G_c$, which is not part of that corporation's network to connect to $G_p$ and become part of the VPN. To that purpose, standard host-to-host CCN authentication mechanisms such as \cite{} can be used to authenticate $G_p$ and $G_c$ to each other. This must be performed before any VPN communication to make sure that only the appropriate parties are communicating under the CCVPN architecture. We discuss the evaluation and specification of gateway-to-gateway authetication protocols as future work (see Sec.~\ref{conclusion}).

@@

\todo{TODO: Introductory text about the sec analysis}

@@

\textit{\textbf{Proof--} Suppose that Claim~\ref{theo1} is false. Then there exists a polynomial adversary $Adv$ capable of guessing the bit $b$ of Definition~\ref{def1} with non-negligible advantage, when given $I_e^b = Encapsulate(I_p^b)$ with $b \leftarrow \{0,1\}$ chosen at random. We show that if such adversary exists he can be used to construct a polinomial adversary $AdvCPA$ which breaks the CPA-security of $Enc_{pk}$. $AdvCPA$ plays the CPA-security game with a challenger sending him two messages $m^0$ and $m^1$. Following the CPA-security game, the challenger randomly chooses a value for the bit $b' \leftarrow \{0,1\}$ and gives back $C = Enc_{pk}(m^{b'})$ to $AdvCPA$. To break the CPA-security $AdvCPA$ must be able to guess the value of the bit $b'$ with non-negligible advantage. To that purpose $AdvCPA$ can query the challenger for the encryptions of $m^0$ and $m^1$ ($c^0 = Enc_{pk}(m^0)$ and $c^1 = Enc_{pk}(m^1)$) and then construct two interests $I_e^0 = createNewInterest(Gp_{name}, c^0)$ and $I_e^1 = createNewInterest(Gp_{name}, c^1)$, using the same $createNewInterest$ function used by algorithm~\ref{alg:interestEncap}, which is public (notice that $Gp_{name}$ is also public). Finally, $AdvCPA$ gives $I_e^0$ and $I_e^1$ as input to $Adv$ and outputs whatever $Adv$ outputs. Since under our assumption $Adv$ guesses the bit $b$ with non-negligible advantage, then $AdvCPA$ breaks the CPA-security of $Enc_{pk}$. But this violates the hypothesis of Claim~\ref{theo1} and, therefore, such $Adv$ cannot exist.
}

@@

\textbf{\textit{Proof--}}
\todo{TODO}

>>>>

Another use case for CCVPN is the traditional VPN use case, in which two physically separated local networks (for instances to offices of the same company in different countries) should virtually behave as a private local network. In that case, it is necessary to prevent that a given $G_c$, which is not part of that corporation's network to connect to $G_p$ and become part of the VPN. To that purpose, standard host-to-host CCN authentication mechanisms such as \cite{} can be used to authenticate $G_p$ and $G_c$ to each other. This must be performed before any VPN communication to make sure that only the appropriate parties are communicating under the CCVPN architecture. We leave the evaluation and specification of gateway-to-gateway authentication protocols as future work (see Sec.~\ref{sec:conclusion}).

@@

In this section we analyze the security of CCVPN. Our main security goal is
preventing an adversary from learning any information about the contents of
packets traversing a CCVPN tunnel. Formally, this translates into semantic
security of all traffic, modulo what can be inferred via traffic analysis.
A consequence of this property is that an off-path adversary, i.e., one that is
not in the consumer or producer domain, is unable to forge packets with
non-negligible probability. Our analysis relies on arguments in the standard
security model. It consists of assessing the security of the interest and
content encapsulation algorithms.

@@

\textbf{Proof--} Suppose that Claim~\ref{theo1} is false. Then there exists a polynomial adversary $Adv$ capable of guessing the bit $b$ of Definition~\ref{def1} with non-negligible advantage, when given $I_e^b = Encapsulate(I_p^b)$ with $b \leftarrow \{0,1\}$ chosen at random. We show that if such adversary exists he can be used to construct a polinomial adversary $AdvCPA$ which breaks the CPA-security of $Enc_{pk}$. $AdvCPA$ plays the CPA-security game with a challenger sending him two messages $m^0$ and $m^1$. Following the CPA-security game, the challenger randomly chooses a value for the bit $b' \leftarrow \{0,1\}$ and gives back $C = Enc_{pk}(m^{b'})$ to $AdvCPA$. To break the CPA-security $AdvCPA$ must be able to guess the value of the bit $b'$ with non-negligible advantage. To that purpose $AdvCPA$ can query the challenger for the encryptions of $m^0$ and $m^1$ ($c^0 = Enc_{pk}(m^0)$ and $c^1 = Enc_{pk}(m^1)$) and then construct two interests $I_e^0 = createNewInterest(Gp_{name}, c^0)$ and $I_e^1 = createNewInterest(Gp_{name}, c^1)$, using the same $createNewInterest$ function used by algorithm~\ref{alg:interestEncap}, which is public (notice that $Gp_{name}$ is also public). Finally, $AdvCPA$ gives $I_e^0$ and $I_e^1$ as input to $Adv$ and outputs whatever $Adv$ outputs. Since under our assumption $Adv$ guesses the bit $b$ with non-negligible advantage, then $AdvCPA$ breaks the CPA-security of $Enc_{pk}$. But this violates the hypothesis of Claim~\ref{theo1} and, therefore, such $Adv$ cannot exist.

@@

\textit{Proof--}This follows directly from the definition of CCA security and the
argument in the above proof.

### 2017-04-06 paper/ccvpn.tex
Updates
new scripts for 1x1 and nxn
some results on n x n

\usepackage[tight,footnotesize]{subfigure}
\usepackage{fixltx2e}

@@

\usepackage{algorithm2e}
\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\begin{IEEEkeywords}
%Human Mobility, Group Detection, Group Dynamics, Periodicity, Opportunistic Routing.
\end{IEEEkeywords}

@@

\input{01-introduction}
\input{02-overview}
\input{03-related}
\input{04-design}
\input{05-sec-analysis}
\input{06-perf-analysis}
\input{07-experiment}
%\input{08-security}

\section{Conclusion}\label{conclusion}
\todo{TODO}

>>>>

\usepackage{subfigure}
\usepackage{fixltx2e}

@@

\usepackage{algorithm2e}
%\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\begin{IEEEkeywords}
Content-Centric Networking, VPN, Tunneling
\end{IEEEkeywords}

@@

\input{01-introduction}
\input{02-overview}
\input{03-related}
\input{04-design}
\input{05-sec-analysis}
\input{06-perf-analysis}
\input{07-experiment}

\section{Conclusion}\label{sec:conclusion}
We presented the design, implementation, and assessment of CCVPN, a scheme and
protocol for building secure and private tunnels in CCN. CCPN allows two namespaces
to be bridged by a tunnel across a public network. Unlike point-to-point tunnels,
such as those enabled by secure session protocols, CCVPN allows many consumers
to share the tunnel to access the private namespace. CCVPN is designed with efficiency
in mind: public-key cryptographic operations are kept to a minimum during normal
operation; symmetric-key packet encapsulation algorithms are used to marshall
packets between gateways. Our experimental evidence indicate that CCVPN offers
modest performance in the presence of a variable number of consumers and producers.
The results suggest that CCVPN could be deployed for private namespace tunneling
in real world CCN deployments.

For future work, we plan to implement the CCNxKE protocol from \ref{ccnxke} as a
way to bootstrap symmetric-key tunnels in CCVPN. We will also integrate CCVPN into
real world testbeds to assess its performance for real-world applications. These
include video streaming and large-scale content dissemination applications.
